### 2014-02-24 thesis/src/chapters/chapter-summary.tex
Thesis: summary v3

% tutaj mozna by wymienic krotko rozwiazania czyli ze autonomiczny, vertykalny na konetenerach - i chyba tyle
Cloud-SAP derives ability to conduct self-monitoring, analysing, planning and executing from mature and widely respected model of an autonomic system.

@@

All tests of the platform were not simulated on any software, but conducted on the real hardware forming a home-made data center. Tests were chosen and design so as to reflect at the highest possible rate real business use cases. Their results show considerable potential of the proposed solution.

TODO co z OpenVZ--KVM?, hmm to jest wpisane pod vertical scaling, mozna by ewentualnie jakos wydzielic te poziomy skalowania i je opisac

\section{Future work}
As the provided implementation cannot be regarded as a fully fledged one, there is a need to implement a system with the advanced algorithms regarding actions in a control loop of autonomic managers such as:
\begin{itemize}
  \item prediction
  \item prioritization
  \item application self-tuning
\end{itemize}
This will enable to conduct more insightful tests of the architecture and prove its usefulness.

Having more mature platform implemented, next step should be to engage communities working on Open Source cloud platform such as OpenNebula, OpenStack or Eucalyptus. It is expected that such cooperation broaden pool of supported cloud providers and thus truly enable diversified federation of clouds.

% moze cos o wyzwaniach z tym zwiazanych, ze trzeba sie dogadac, ustalic wspolny model, format

>>>>

@@

All tests of the platform were not simulated on any software, but conducted on the real hardware forming a home-made data center. Tests were chosen and design so as to reflect at the highest possible rate real business use cases. Their results show considerable potential of the proposed solution. Nevertheless, we did not manage to evaluate implementation in a real-world scenario that entails using enterprise-level application such as the ones based on Java Enterprise Edition.

\section{Future work}
As the provided implementation cannot be regarded as a fully fledged one, there is a need to implement a system with the advanced algorithms regarding actions in a control loop of autonomic managers such as:
\begin{inparaenum}[1)]
  \item prediction
  \item service prioritization
  \item application self-tuning
\end{inparaenum}
This will enable to conduct more insightful tests of the architecture and prove its usefulness.

Beside this, the implementation should became a business-ready product instead of being simply a proof-of-concept. What should be done to enact it is to:
\begin{itemize}
 \item enrich Cloud-SAP architecture with a number of financial aspects such as service maintenance cost, policy and customer oriented billings (i.e. fee should take into account customer-specified policy or customer himself).
 \item evaluate solution against real-world benchmarks such as SPECweb96, SPECweb99 or TPC-C
\end{itemize}
Due to Cloud-SAP flexibility, above-mentioned features should be easily and seamlessly incorporated in proposed model.

Having more mature platform implemented and tested, next step should be to engage communities working on Open Source cloud platform such as OpenNebula, OpenStack or Eucalyptus. It is expected that such cooperation broaden pool of supported cloud providers and thus truly enable diversified federation of clouds. However, for cloud providers to cooperate, there is a need for discussion and consideration regarding aspects such as authentication, authorization, resource
 access, resource discovery, to name a few.
